### 2019-01-17 Draft/Draft.tex
Added Draft folder which will contain the working paper along with parts folder which will contain different parts of the paper, updated abstract

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Draft of Paper for SER - 574}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.

\author{Ruben Acuna}
\affiliation{%
  \institution{Arizona State University}
  \streetaddress{Tempe}
  \city{Phoenix}
  \country{USA}}
\email{ruben.acuna@asu.edu}

\author{Sarthak Tiwari}
\affiliation{%
  \institution{Arizona State University}
  \streetaddress{Tempe}
  \city{Phoenix}
  \country{USA}}
\email{sarthak.tiwari@asu.edu}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Ruben and Sarthak, et al.}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}

\input{./Parts/Abstract}

\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%
% A "teaser" image appears between the author and affiliation information and the body 
% of the document, and typically spans the page. 
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a consistent \LaTeX\ style for use across ACM publications, and incorporates accessibility and metadata-extraction functionality necessary for future Digital Library endeavors. Numerous ACM and SIG-specific \LaTeX\ templates have been examined, and their unique features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable guide to the process of preparing your work for publication. If you have published with ACM before, this document provides insight and instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles for any ACM publication --- conference or journal, and for any stage of publication, from review to final ``camera-ready'' copy, to the author's own version, with {\it very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can be used to prepare many different kinds of documentation --- a double-blind initial submission of a full-length technical paper, a two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready'' journal article, a SIGCHI Extended Abstract, and more --- all by selecting the appropriate {\it template style} and {\it template parameters}.

This document will explain the major features of the document class. For further information, the {\it \LaTeX\ User's Guide} is available from \url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is the {\it template style} which corresponds to the kind of publication or SIG publishing the work. This parameter is enclosed in square brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\it template style} to be used in formatting your work, there are a number of {\it template parameters} which modify some part of the applied template style. A complete list of these parameters can be found in the {\it \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind'' conference submission. Anonymizes the work and includes line numbers. Use with the \verb|\acmSubmissionID| command to print the submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the source file: \verb|\documentclass[sigconf,screen]{acmart}|.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting margins, typeface sizes, line spacing, paragraph and list definitions, and the use of the \verb|\vspace| command to manually adjust the vertical spacing between elements of your work --- is not allowed.

{\bf Your document will be returned to you for revision if modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the ``Libertine'' typeface family. Your \TeX\ installation should include this set of packages. Please do not substitute other typefaces. The ``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used, as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately - \url{https://capitalizemytitle.com/} has useful rules for capitalization. Use the {\verb|title|} command to define the title of your work. If your work has a subtitle, define it with the {\verb|subtitle|} command.
Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used in the page headers, to prevent overlapping text. The \verb|title| command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata identification. Multiple authors may share one affiliation. Authors' names should not be abbreviated; use full first names wherever possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note to apply to multiple authors --- for example, if the first two authors of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of the list of authors to be used in the page headers, to prevent overlapping text. The following command should be placed just after the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all of the authors' names, which may result in overlapping text in the page headers.

The article template's documentation, available at  \url{https://www.acm.org/publications/proceedings-template}, has a complete explanation of these commands and tips for their effective use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights form. Depending on the kind of work, and the rights management choice made by the author, this may be copyright transfer, permission, license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a copy of the completed rights form once it has been submitted. This form contains \LaTeX\ commands that must be copied into the source document. When the document source is compiled, these commands and their parameters add formatted text to several areas of the final document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several works for an event, make sure to use the correct set of commands with each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful taxonomic tools for you to help readers find your work in an online search.

The ACM Computing Classification System --- \url{https://www.acm.org/publications/class-2012} --- is a set of classifiers and concepts that describe the computing discipline. Authors can select entries from this classification system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases of the authors' choosing, providing a more flexible way of describing the research being presented.

CCS concepts and user-defined keywords are required for all short- and full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands: \verb|section|, \verb|subsection|, \verb|subsubsection|, and \verb|paragraph|. They should be numbered; do not remove the numbering from the commands.

Simulating a sectioning command by setting the first word or words of a paragraph in boldface or italicized text is {\bf not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|'' package --- \url{https://ctan.org/pkg/booktabs} --- for preparing high-quality tables.

Table captions are placed {\it above} the table.

Because tables cannot be split across pages, the best placement for them is typically the top of the page nearest their initial cite.  To ensure this proper ``floating'' placement of tables, use the environment \textbf{table} to enclose the table's contents and the table caption.  The contents of the table itself must go in the \textbf{tabular} environment, to be aligned properly in rows and columns, with the desired horizontal and vertical rules.  Again, detailed instructions on \textbf{tabular} material are found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which Table~\ref{tab:freq} is included in the input file; compare the placement of the table here with the table in the printed output of this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's live area, use the environment \textbf{table*} to enclose the table's contents and the table caption.  As with a single-column table, this wide table will ``float'' to a location deemed more desirable. Immediately following this sentence is the point at which Table~\ref{tab:commands} is included in the input file; again, it is instructive to compare the placement of the table here with the table in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
construction or with the short form \texttt{\$\,\ldots\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX\@; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or more images can be placed within a figure. If your figure contains third-party material, you must clearly identify it as such, as shown in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing, Inc. [Public domain], via Wikimedia Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to the reader. Figure captions go below the figure. Your figures should {\bf also} include a description suitable for screen readers, to assist the visually-challenged to better understand your work.

Figure captions are placed {\it below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that are placed after all author and affiliation information, and before the body of the article, spanning the page. If you wish to have such a figure in your article, place the command immediately before the \verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's references is strongly recommended. Authors' names should be complete --- use full first names (``Donald E. Knuth'') not initials (``D. E. Knuth'') --- and the salient identifying features of a reference should be included: title, year, volume, number, pages, article DOI, etc.

The bibliography is included in your source document with these two commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|'' suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of ACM publications have citations and references formatted in the ``author year'' style; for these exceptions, please include this command in the {\bf preamble} (before ``\verb|\begin{document}|'') of your \LaTeX\ source: 
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

Some examples.  A paginated journal article \cite{Abril07}, an enumerated journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation \cite{Editor00} followed by the same example, however we only output the series if the volume number is given \cite{Editor00a} (so Editor00a's series should NOT be present since it has no vol. no.),
a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97}, an article in a proceedings (of a conference, symposium, workshop for example) (paginated proceedings article) \cite{Andler79}, a proceedings article with all possible elements \cite{Smith10}, an example of an enumerated proceedings article \cite{VanGundy07}, an informally published work \cite{Harel78}, a doctoral dissertation \cite{Clarkson85}, a master's thesis: \cite{anisi03}, an online document / world wide web resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and (Case 3) a patent \cite{JoeScientist001}, work accepted for publication \cite{rous08}, 'YYYYb'-test for prolific author \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might contain 'duplicate' DOI and URLs (some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton: multi-volume works as books \cite{MR781536} and \cite{MR781537}. A couple of citations with DOIs: \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected during the article metadata extraction phase, and to ensure consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the ``\verb|\end{document}|'' command at the conclusion of your source document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not numbered. This document has two appendices, demonstrating the section and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and not in Word) produces a landscape-orientation formatted article, with a wide left margin. Three environments are available for use with the ``\verb|sigchi-a|'' template style, and produce formatted output in the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%
% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

% 
% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi malesuada, quam in pulvinar varius, metus nunc fermentum urna, id sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non ipsum convallis congue hendrerit vitae sapien. Donec at laoreet eros. Vivamus non purus placerat, scelerisque diam eu, cursus ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis enim maximus. Vestibulum gravida massa ut felis suscipit congue. Quisque mattis elit a risus ultrices commodo venenatis eget dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar massa et mattis lacinia.

\end{document}

### 2019-01-17 Draft/Parts/Abstract.tex
Added Draft folder which will contain the working paper along with parts folder which will contain different parts of the paper, updated abstract

With the boom in the use of agile process model, imperfect implementations of agile are frequently being seen, out of which the problem of inter-team communication in agile teams is one of the most common issue. An agile team by its definition is a group of people who are self-sufficient to bring their responsibilities to closure, the interaction between different teams is thus considered minimal in most projects implementing agile. This causes problems when the integration of end-products of different teams is carried out. In this paper we have taken a detailed look at this problem and how we can mitigate this.

### 2019-01-18 Draft/Draft.tex
Added Introduction section and some references

@@
 % presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{Agile, Software Engineering, Process Models, Inter-team, Management}
 
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a consistent \LaTeX\ style for use across ACM publications, and incorporates accessibility and metadata-extraction functionality necessary for future Digital Library endeavors.
-Numerous ACM and SIG-specific \LaTeX\ templates have been examined, and their unique features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable guide to the process of preparing your work for publication.
-If you have published with ACM before, this document provides insight and instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles for any ACM publication --- conference or journal, and for any stage of publication, from review to final ``camera-ready'' copy, to the author's own version, with {\it very} few changes to the source.
+\input{./Parts/Introduction}
 

### 2019-01-18 Draft/Parts/Introduction.tex
Added Introduction section and some references

As mentioned in the Agile Manifesto \cite{beck2001agile}, Individuals and Interactions are given more value than the processes and tools. At the same time, an agile team is supposed to contain all that is required for them to do their work, thus interactions no matter how valuable usually are done intra-team only. Thus, when a situation arrives where two or more agile teams need to work together to achieve a common goal the usual approach taken by companies fail. The agile approach of interacting in-person fails due to a few reasons such as the vertical structure of the company organization and the existence of middle managers \cite{dzone_article}. This large number of intermediaries in inter team communication causes the process to crumble and fall apart as it takes longer than usual time for messages to reach their destination then what agile can afford.
This problem is harder to fix as this is so embedded in the working culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required. And that’s where the approaches listed in the article comes in. We have collected a couple of approaches which if implemented efficiently results in a more stable and functioning agile process model. Thus, in the following sections we will be explaining couple of approaches we came across.

### 2019-01-19 Draft/Draft.tex
Added Proposed Approach Section and one of its subsection

@@
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can be used to prepare many different kinds of documentation --- a double-blind initial submission of a full-length technical paper, a two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready'' journal article, a SIGCHI Extended Abstract, and more --- all by selecting the appropriate {\it template style} and {\it template parameters}.
-
-This document will explain the major features of the document class.
-For further information, the {\it \LaTeX\ User's Guide} is available from \url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is the {\it template style} which corresponds to the kind of publication or SIG publishing the work.
-This parameter is enclosed in square brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\it template style} to be used in formatting your work, there are a number of {\it template parameters} which modify some part of the applied template style.
-A complete list of these parameters can be found in the {\it \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind'' conference submission.
-Anonymizes the work and includes line numbers.
-Use with the \verb|\acmSubmissionID| command to print the submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the source file: \verb|\documentclass[sigconf,screen]{acmart}|.
+\input{./Parts/Proposed_Approach}
 

### 2019-01-19 Draft/Parts/Introduction.tex
Added Proposed Approach Section and one of its subsection

@@
 Thus, in the following sections we will be explaining couple of approaches we came across.
+\linebreak
+In Section ~\ref{sec:proc_impv} we will be explaining the improvements that can be made to the process and team structures to get better collaboration out of the team involved.
+\linebreak
+In section 3 we will be explaining the enhancements that can be done in the technology stack being used and in the different ways in which technology can help in improving the process.

### 2019-01-19 Draft/Parts/Proposed_Approach.tex
Added Proposed Approach Section and one of its subsection

\section{Process Improvements} 
\label{sec:proc_impv}
	There are many small changes that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase. These changes are to be made part of the entire process and are not to be implemented only in the end.

\subsection{Changes in standups}
	One of the most critical aspect of agile process model is to have daily standups which are the platform serving the purpose of letting each team member know the work being done in the other parts of the team and corelate it with the work being done by them. This results in escalation of differences between the development early in the process and prevents end moment discovery of mismatches in interfaces and such. In the case of multiple agile teams this problem is compounded as usually a daily stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other. This can be resolved by having a representative of each concerned team being present in the daily standup thus letting each team know the status of other teams.

\subsection{Changes to Product Owner}
	Though in usual implementations the product owner is responsible for agile teams under his supervision, in large projects with multiple agile teams where a number of product owners are present sometimes over time the vision of the owners may get too distinct from each other thus pushing the development track in different directions. This can be limited by having regular meetings of product owners where the scope and vision of the project could be synced again. This can be a bi-weekly or monthly meeting depending on the size of the project.

\subsection{Changes in Planning Sessions}
	All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.

### 2019-01-19 Draft/Parts/Introduction.tex
Added another section to proposed approach

--- 2019-01-18 Draft/Parts/Introduction.tex
@@
 Thus, in the following sections we will be explaining couple of approaches we came across.
+\linebreak
+\linebreak
+In Section ~\ref{sec:proc_impv}, we will be explaining the improvements that can be made to the process and team structures to get better collaboration out of the team involved.
+\linebreak
+\linebreak
+In Section ~\ref{sec:tech_impv}, we will be explaining the enhancements that can be done in the technology stack being used and in the different ways in which technology can help in improving the process.

### 2019-01-19 Draft/Parts/Proposed_Approach.tex
Added another section to proposed approach

@@
 	All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
+
+\section{Technology Improvements} 
+\label{sec:tech_impv}
+	A good technology stack can be a powerful tool in maintaining a widely distributed team.
+Good communication and management tools can help the teams in keeping track of things that they need to do so that other teams can work as intended.
+The following are some of the areas where the technology can assist the teams in making a more efficient agile process environment.
+
+\subsection{Communication Tools} As agile focuses on personal interaction with highest importance given to face-to-face conversation, conferencing tools such as video conferencing and WebEx etc.
+can help the team interactions become more fluid and clearer.
+They also make the communication real-time thus removing the lag in process due to time spent in communicating ideas across teams.
+
+\subsection{Integration Tools} Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.

### 2019-01-20 Draft/Parts/Main.tex
Added main section

--- 2019-01-19 Draft/Parts/Proposed_Approach.tex
@@
 \subsection{Integration Tools} Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.
+
+\section{Importance of Architecture/Design}
+\label{sec:imp_of_dsgn}
+As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt.
+But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision.
+The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners.
+The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.

### 2019-01-20 Draft/Draft.tex
Added main section
Added Conclusion and removed extra page segments

@@
 %
-% A "teaser" image appears between the author and affiliation information and the body 
-% of the document, and typically spans the page. 
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
-
-%
 % This command processes the author and affiliation and title information and builds
@@
 
-\input{./Parts/Proposed_Approach}
+\input{./Parts/Main}
 
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting margins, typeface sizes, line spacing, paragraph and list definitions, and the use of the \verb|\vspace| command to manually adjust the vertical spacing between elements of your work --- is not allowed.
-
-{\bf Your document will be returned to you for revision if modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the ``Libertine'' typeface family.
-Your \TeX\ installation should include this set of packages.
-Please do not substitute other typefaces.
-The ``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used, as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately - \url{https://capitalizemytitle.com/} has useful rules for capitalization.
-Use the {\verb|title|} command to define the title of your work.
-If your work has a subtitle, define it with the {\verb|subtitle|} command.
-Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used in the page headers, to prevent overlapping text. The \verb|title| command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata identification.
-Multiple authors may share one affiliation.
-Authors' names should not be abbreviated; use full first names wherever possible.
-Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note to apply to multiple authors --- for example, if the first two authors of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of the list of authors to be used in the page headers, to prevent overlapping text.
-The following command should be placed just after the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all of the authors' names, which may result in overlapping text in the page headers.
-
-The article template's documentation, available at  \url{https://www.acm.org/publications/proceedings-template}, has a complete explanation of these commands and tips for their effective use.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights form.
-Depending on the kind of work, and the rights management choice made by the author, this may be copyright transfer, permission, license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a copy of the completed rights form once it has been submitted.
-This form contains \LaTeX\ commands that must be copied into the source document.
-When the document source is compiled, these commands and their parameters add formatted text to several areas of the final document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several works for an event, make sure to use the correct set of commands with each of the works.
+\input{./Parts/Conclusion}
 
@@
 
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands: \verb|section|, \verb|subsection|, \verb|subsubsection|, and \verb|paragraph|.
-They should be numbered; do not remove the numbering from the commands.
-
-Simulating a sectioning command by setting the first word or words of a paragraph in boldface or italicized text is {\bf not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|'' package --- \url{https://ctan.org/pkg/booktabs} --- for preparing high-quality tables.
-
-Table captions are placed {\it above} the table.
-
-Because tables cannot be split across pages, the best placement for them is typically the top of the page nearest their initial cite.
-To ensure this proper ``floating'' placement of tables, use the environment \textbf{table} to enclose the table's contents and the table caption.
-The contents of the table itself must go in the \textbf{tabular} environment, to be aligned properly in rows and columns, with the desired horizontal and vertical rules.
-Again, detailed instructions on \textbf{tabular} material are found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which Table~\ref{tab:freq} is included in the input file; compare the placement of the table here with the table in the printed output of this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's live area, use the environment \textbf{table*} to enclose the table's contents and the table caption.
-As with a single-column table, this wide table will ``float'' to a location deemed more desirable.
-Immediately following this sentence is the point at which Table~\ref{tab:commands} is included in the input file; again, it is instructive to compare the placement of the table here with the table in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin\,\ldots{\char'134}end}
-construction or with the short form \texttt{\$\,\ldots\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX\@; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures.
-One or more images can be placed within a figure.
-If your figure contains third-party material, you must clearly identify it as such, as shown in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing, Inc. [Public domain], via Wikimedia Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to the reader.
-Figure captions go below the figure.
-Your figures should {\bf also} include a description suitable for screen readers, to assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\it below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that are placed after all author and affiliation information, and before the body of the article, spanning the page.
-If you wish to have such a figure in your article, place the command immediately before the \verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's references is strongly recommended.
-Authors' names should be complete --- use full first names (``Donald E.
-Knuth'') not initials (``D.
-E.
-Knuth'') --- and the salient identifying features of a reference should be included: title, year, volume, number, pages, article DOI, etc.
-
-The bibliography is included in your source document with these two commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|'' suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default.
-A small number of ACM publications have citations and references formatted in the ``author year'' style; for these exceptions, please include this command in the {\bf preamble} (before ``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-Some examples.
-A paginated journal article \cite{Abril07}, an enumerated journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec.
-document)
-\cite{Harel79}, a divisible-book such as an anthology or compilation \cite{Editor00} followed by the same example, however we only output the series if the volume number is given \cite{Editor00a} (so Editor00a's series should NOT be present since it has no vol.
-no.),
-a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97}, an article in a proceedings (of a conference, symposium, workshop for example) (paginated proceedings article) \cite{Andler79}, a proceedings article with all possible elements \cite{Smith10}, an example of an enumerated proceedings article \cite{VanGundy07}, an informally published work \cite{Harel78}, a doctoral dissertation \cite{Clarkson85}, a master's thesis: \cite{anisi03}, an online document / world wide web resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and (Case 3) a patent \cite{JoeScientist001}, work accepted for publication \cite{rous08}, 'YYYYb'-test for prolific author \cite{SaeediMEJ10} and \cite{SaeediJETC10}.
-Other cites might contain 'duplicate' DOI and URLs (some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}.
-Boris / Barbara Beeton: multi-volume works as books \cite{MR781536} and \cite{MR781537}.
-A couple of citations with DOIs: \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}.
-Online citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to individuals and groups that assisted in the research and the preparation of the work should be included in an acknowledgment section, which is placed just before the reference section in your document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected during the article metadata extraction phase, and to ensure consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the ``\verb|\end{document}|'' command at the conclusion of your source document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not numbered. This document has two appendices, demonstrating the section and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and not in Word) produces a landscape-orientation formatted article, with a wide left margin.
-Three environments are available for use with the ``\verb|sigchi-a|'' template style, and produce formatted output in the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%
-% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
-% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
 %
@@
 
-% 
-% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi malesuada, quam in pulvinar varius, metus nunc fermentum urna, id sollicitudin purus odio sit amet enim.
-Aliquam ullamcorper eu ipsum vel mollis.
-Curabitur quis dictum nisl.
-Phasellus vel semper risus, et lacinia dolor.
-Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque.
-Etiam auctor sodales ligula, non varius nibh pulvinar semper.
-Suspendisse nec lectus non ipsum convallis congue hendrerit vitae sapien.
-Donec at laoreet eros.
-Vivamus non purus placerat, scelerisque diam eu, cursus ante.
-Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui.
-Suspendisse sagittis tortor a nulla mollis, in pulvinar ex pretium.
-Sed interdum orci quis metus euismod, et sagittis enim maximus.
-Vestibulum gravida massa ut felis suscipit congue.
-Quisque mattis elit a risus ultrices commodo venenatis eget dui.
-Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar massa et mattis lacinia.
-
 \end{document}

### 2019-01-20 Draft/Parts/Conclusion.tex
Added Conclusion and removed extra page segments

\section{Conclusion} 
\label{sec:conclusion}
As we have seen, the issue of inter-team communication can be a big problem in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked. To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture / design which is available to all the teams and thus provides a common vision to all the teams involved.

### 2019-01-20 Draft/Parts/Main.tex
Added Conclusion and removed extra page segments

@@
 \label{sec:proc_impv}
-	There are many small changes that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
+	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
 These changes are to be made part of the entire process and are not to be implemented only in the end.

### 2019-01-20 Draft/Parts/Introduction.tex
Added main section
Changed files to use one line per sentence (better change tracking).
Introduction: misc changes.

--- 2019-01-18 Draft/Parts/Introduction.tex
@@
-As mentioned in the Agile Manifesto \cite{beck2001agile}, Individuals and Interactions are given more value than the processes and tools.
-At the same time, an agile team is supposed to contain all that is required for them to do their work, thus interactions no matter how valuable usually are done intra-team only.
-Thus, when a situation arrives where two or more agile teams need to work together to achieve a common goal the usual approach taken by companies fail.
+%Introduction (Introducing the topic)
+
+%introduce agile
+Recently, agile approaches have become popular in software development.
+As outlined in the Agile Manifesto \cite{beck2001agile}, an agile process gives individuals and interactions value over processes and tools.
+%An agile team is supposed to contain all that is required for them to do their work, thus interactions no matter how valuable usually are done intra-team only.
+As software grows in complexity, situations arise where multiple agile teams need to work together to achieve a common goal.
+%explain what we are doing
+In this paper we survey several the issues that can arise when agile teams must work together.
+We also discuss approaches, which if implemented correctly, provide a more robust and functional process for inter-team agile development. 
+%
+%introduce the need to scale to multiple agile teams
+%However, the stucture of agile team does not lend itself to large teams, and so applying the agile process requires mutiple teams.
+Although an independent team may use an agile process with ease, additional considerations are required for complex systems where running multiple agile teams in parallel becomes necessary.
 The agile approach of interacting in-person fails due to a few reasons such as the vertical structure of the company organization and the existence of middle managers \cite{dzone_article}.
-This large number of intermediaries in inter team communication causes the process to crumble and fall apart as it takes longer than usual time for messages to reach their destination then what agile can afford.
-This problem is harder to fix as this is so embedded in the working culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required.
-And that’s where the approaches listed in the article comes in.
-We have collected a couple of approaches which if implemented efficiently results in a more stable and functioning agile process model.
-Thus, in the following sections we will be explaining couple of approaches we came across.
+
+%introduce potential issues (com, arch)
+The transition to multiple teams increases the importance of inter-team communication, from simple interpersonal communication, to system specification. 
+%arch
+In an agile process, where Big Design Up-front may typically be avoided, the move to multiple teams motivates a stronger need to communicate design decisions.
+In order for sucessful integration of techonological components, system elements must have well defined functional specifications, and interfaces.
+%com
+This large number of intermediaries in inter-team communication causes the process to fall apart as it takes longer than usual time for messages to reach their destination then what agile can afford.
+This problem is difficult to fix as this is so embedded in the working agile culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required.
+
+%outline of rest of paper
+This document is separated into five sections: Introduction, Process Inprovements, Technology Improvements, Importance of Architecture \& Design, and Conclusion. 
+In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
+In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication.
+In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

### 2019-01-20 Draft/Draft.tex
Add title. Make author information more formal.
Removing ACM reference formatting.

@@
 % The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
-\title{Draft of Paper for SER - 574}
+\title{Agile Inter-team Software Development}
 
@@
 
-\author{Ruben Acuna}
+\author{Sarthak Tiwari}
 \affiliation{%
+  \department{School of Computing, Informatics, and Decision Systems Engineering}
   \institution{Arizona State University}
-  \streetaddress{Tempe}
-  \city{Phoenix}
+  \city{Tempe}
+  \state{Arizona}
+  \country{USA}}
+\email{sarthak.tiwari@asu.edu}
+
+\author{Ruben Acu{\~n}a}
+\affiliation{%
+  \department{School of Computing, Informatics, and Decision Systems Engineering}
+  \institution{Arizona State University}
+  \city{Tempe}
+  \state{Arizona}
   \country{USA}}
 \email{ruben.acuna@asu.edu}
-
-\author{Sarthak Tiwari}
-\affiliation{%
-  \institution{Arizona State University}
-  \streetaddress{Tempe}
-  \city{Phoenix}
-  \country{USA}}
-\email{sarthak.tiwari@asu.edu}
 
@@
 % of authors' names for this purpose.
-\renewcommand{\shortauthors}{Ruben and Sarthak, et al.}
+\renewcommand{\shortauthors}{Tiwari and Acu{\~n}a}
+
+\settopmatter{printacmref=false}						%RA: get rid of dumb ACM reference format BLAH BLAH
 
@@
 % presented. Separate the keywords with commas.
-\keywords{Agile, Software Engineering, Process Models, Inter-team, Management}
+\keywords{Agile, Software Engineering, Software Development, Process Models, Inter-team, Management}
 

### 2019-01-20 Draft/Parts/Main.tex
Changed files to use one line per sentence (better change tracking).
Added content from Spotify reference.

@@
+\section{NAME ME} 
+For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
+The basic element of the development organization at Spotify is the Squad, analgous to a Scrum team.
+Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
+Squads in related areas are grouped together into Tribes.
+Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
+
+%add image
+
+\subsection{NAME ME}
+%social fixes
+A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
+At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
+This leads to an environment where an informal exchange of information on the Tribes work will occur.
+%second problem
+Consider another secnario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team.
+Without communication, these team members would perform redundant work.
+To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers inviduals with simular roles accross different Squads.
+
 \section{Process Improvements} 
@@
 
-\section{Importance of Architecture/Design}
-\label{sec:imp_of_dsgn}
+\section{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
+%Why is Design/Architecture so important when doing this?
+
 As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt.
@@
 The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.
+%non specification fix
+Spotify addresses this issue with a more organizational approach by defining a "system owner" role \cite{kniberg12}.
+This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.

### 2019-01-20 Draft/Draft.tex
Added image for Spotify. Fix CCS information.

@@
 \documentclass[sigplan,screen]{acmart}
+
+\usepackage{graphicx}
 
@@
 \setcopyright{acmlicensed}
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
+\acmConference[SER574 '19]{SER574 '19: Advanced Software Design}{January 20, 2019}{Mesa, AZ}
+\acmBooktitle{SER574 '19: Advanced Software Design, January 20, 2019, Mesa, AZ}
+\acmPrice{1500.00}
 \acmDOI{10.1145/1122445.1122456}
@@
 
-\settopmatter{printacmref=false}						%RA: get rid of dumb ACM reference format BLAH BLAH
+%RA: remove the BLAH BLAH
+%see  https://tex.stackexchange.com/questions/346292/how-to-remove-conference-information-from-the-acm-2017-sigconf-template
+%\settopmatter{printacmref=false}						   %ACM reference format BLAH BLAH
+\renewcommand\footnotetextcopyrightpermission[1]{} %ACM premission thing
+%\pagestyle{plain}														 %ACM running header
 
@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10011007.10011074.10011081.10011082.10011083</concept_id>
+<concept_desc>Software and its engineering~Agile software development</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+<concept_id>10011007.10011074.10011134.10011135</concept_id>
+<concept_desc>Software and its engineering~Programming teams</concept_desc>
 <concept_significance>300</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+<concept_id>10003456.10003457.10003490.10003491.10003492</concept_id>
+<concept_desc>Social and professional topics~Project management techniques</concept_desc>
+<concept_significance>300</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Software and its engineering~Agile software development}
+\ccsdesc[300]{Software and its engineering~Programming teams}
+\ccsdesc[300]{Social and professional topics~Project management techniques}
 
@@
 
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful taxonomic tools for you to help readers find your work in an online search.
-
-The ACM Computing Classification System --- \url{https://www.acm.org/publications/class-2012} --- is a set of classifiers and concepts that describe the computing discipline.
-Authors can select entries from this classification system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases of the authors' choosing, providing a more flexible way of describing the research being presented.
-
-CCS concepts and user-defined keywords are required for all short- and full-length articles, and optional for two-page abstracts.
-
 %

### 2019-01-20 Draft/Parts/Main.tex
Added image for Spotify. Fix CCS information.

@@
-\section{NAME ME} 
+\section{Spotify: A Canonical Example} 
 For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
-The basic element of the development organization at Spotify is the Squad, analgous to a Scrum team.
+The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
 Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
 Squads in related areas are grouped together into Tribes. 
+The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
 Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
 
-%add image
+\begin{figure}[h]
+  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
+  \caption{Agile team organization at Spotify \cite{kniberg12}.}
+  \label{fig:spotify_structure}
+\end{figure}
 

### 2019-01-20 Draft/Parts/Main.tex
Realigning sections in main document.

@@
 
-\subsection{NAME ME}
+\subsection{Communication}
 %social fixes
@@
 %second problem
-Consider another secnario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team.
+Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team.
 Without communication, these team members would perform redundant work.
-To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers inviduals with simular roles accross different Squads.
+To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers individuals with similar roles across different Squads.
 
-\section{Process Improvements} 
+\section{NAME ME}
+
+\subsection{Process Improvements} 
 \label{sec:proc_impv}
@@
 
-\subsection{Changes in standups}
-	One of the most critical aspect of agile process model is to have daily standups which are the platform serving the purpose of letting each team member know the work being done in the other parts of the team and corelate it with the work being done by them.
+%Changes in standups
+	One of the most critical aspect of agile process model is to have daily standups which are the platform serving the purpose of letting each team member know the work being done in the other parts of the team and correlate it with the work being done by them.
 	This results in escalation of differences between the development early in the process and prevents end moment discovery of mismatches in interfaces and such.
@@
 
-\subsection{Changes to Product Owner}
+%Changes to Product Owner
 Though in usual implementations the product owner is responsible for agile teams under his supervision, in large projects with multiple agile teams where a number of product owners are present sometimes over time the vision of the owners may get too distinct from each other thus pushing the development track in different directions.
@@
 
-\subsection{Changes in Planning Sessions}
-	All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
+%Changes in Planning Sessions
+All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting.
+This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
 
-\section{Technology Improvements} 
+\subsection{Technology Improvements} 
 \label{sec:tech_impv}
@@
 
-\subsection{Communication Tools} As agile focuses on personal interaction with highest importance given to face-to-face conversation, conferencing tools such as video conferencing and WebEx etc.
+%Communication Tools
+As agile focuses on personal interaction with highest importance given to face-to-face conversation, conferencing tools such as video conferencing and WebEx etc.
 can help the team interactions become more fluid and clearer.
@@
 
-\subsection{Integration Tools} Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.
+%Integration Tools
+Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.
 
-\section{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
+\subsection{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
 %Why is Design/Architecture so important when doing this?

### 2019-01-20 Draft/Parts/Main.tex
Added Parnas72 (cite + text).

@@
 This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.
+
+In addition to specification of system elements, architecture can also be used to empower teams.
+As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
+The latter approach ideal for agile development since this approaches defines system components in terms of design dicisions, which empowers invidual teams.

### 2019-01-20 Draft/Parts/Conclusion.tex
Changed files to use one line per sentence (better change tracking).
Adding transition paragraph for process/tech/arch.

@@
 \label{sec:conclusion}
-As we have seen, the issue of inter-team communication can be a big problem in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
-To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture / design which is available to all the teams and thus provides a common vision to all the teams involved.
+As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
+To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

### 2019-01-20 Draft/Parts/Main.tex
Adding transition paragraph for process/tech/arch.

@@
 \section{NAME ME} 
+The general problem of communication can be tackled from two perspectives.
+First, stakeholders at different levels need to have ways to pass information.
+This can be addressed by adaptions in development process and leveraging technology.
+Second, the quality of communication needs to be accurate.
+This can be addressed by sound system specification through architecture and design.
 

### 2019-01-20 Draft/Parts/Introduction.tex
Updated the introduction section to reflect new sections and updated the section 3 name to proposed approach

@@
 %outline of rest of paper
-This document is separated into five sections: Introduction, Process Inprovements, Technology Improvements, Importance of Architecture \& Design, and Conclusion. 
-In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
-In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication.
-In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.
+This document is separated into four sections: Introduction, Sportify: A Canonical Example, Proposed Approach and Conclusion. 
+In Section ~\ref{sec:spt_ex}, we discuss the a real world example of large scale agile project and show a problem encountered in that.
+In Section ~\ref{sec:prop_appro}, we present some adaptations that can be done in agile process model to resolve the problem discussed.

### 2019-01-20 Draft/Parts/Main.tex
Updated the introduction section to reflect new sections and updated the section 3 name to proposed approach

@@
 \section{Spotify: A Canonical Example} 
+\label{sec:spt_ex} 
 For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
@@
 
-\section{NAME ME} 
+\section{Proposed Approach}
+\label{sec:prop_appro} 
 The general problem of communication can be tackled from two perspectives.

### 2019-01-20 Draft/Parts/Abstract.tex
Changed files to use one line per sentence (better change tracking).
Rewrite abstract.

@@
-With the boom in the use of agile process model, imperfect implementations of agile are frequently being seen, out of which the problem of inter-team communication in agile teams is one of the most common issue.
-An agile team by its definition is a group of people who are self-sufficient to bring their responsibilities to closure, the interaction between different teams is thus considered minimal in most projects implementing agile.
-This causes problems when the integration of end-products of different teams is carried out.
-In this paper we have taken a detailed look at this problem and how we can mitigate this.
+%Problem statement
+As the complexity of software development increases, companies relying on agile processes are asked to apply agile at large scale.
+However, this conflicts with the basic tenets of agile which focus on interaction and flexibility.
+%Proposed Solutions
+A typical solution is to run several agile teams in parallel, with appropriate adaptations in process, technology, and architecture.
+%Contribution/Method
+In this paper, we review the use of agile for large projects, and appropriate adaptations.

### 2019-01-21 Draft/Parts/Abstract.tex
Make abstract more clear.

@@
 As the complexity of software development increases, companies relying on agile processes are asked to apply agile at large scale.
-However, this conflicts with the basic tenets of agile which focus on interaction and flexibility.
+A typical approach is to run several agile teams in parallel, however, this can conflict with the basic tenets of agile which focus on interaction and flexibility.
 %Proposed Solutions
-A typical solution is to run several agile teams in parallel, with appropriate adaptations in process, technology, and architecture.
+A key aspect in this transition is maintaining quality communication to ensure progress, which can be addressed with appropriate adaptations in process, technology, and architecture.
 %Contribution/Method

### 2019-01-21 Draft/Parts/Conclusion.tex
Minor fixes to random stuff.

@@
-\section{Conclusion} 
-\label{sec:conclusion}
+\section{Conclusion}\label{sec:conclusion}
 As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.

### 2019-01-21 Draft/Parts/Main.tex
Minor fixes to random stuff.

@@
 \label{sec:spt_ex} 
-For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
-The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
+For an example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
+The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
 Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
@@
 
-\subsection{Communication}
+\subsection{Communication at Spotify}
 %social fixes
@@
 
-\section{Proposed Approach}
+\section{Communication in Inter-team Development}
 \label{sec:prop_appro} 
@@
 This can be addressed by sound system specification through architecture and design.
+%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
+%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
+%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.
 
@@
 
-\subsection{Technology Improvements} 
-\label{sec:tech_impv}
-	A good technology stack can be a powerful tool in maintaining a widely distributed team.
-	Good communication and management tools can help the teams in keeping track of things that they need to do so that other teams can work as intended.
-	The following are some of the areas where the technology can assist the teams in making a more efficient agile process environment.
+\subsection{Technology Approaches} \label{sec:tech_impv}
+Selecting an appropriate technology stack plays an important role maintaining a widely distributed team.
+Technology can help teams in keeping track of things that they need to do so that other teams can work efficiently.
+The following are some of the areas where the technology can enable a more efficient agile process environment.
 
 %Communication Tools
-As agile focuses on personal interaction with highest importance given to face-to-face conversation, conferencing tools such as video conferencing and WebEx etc.
-can help the team interactions become more fluid and clearer.
-They also make the communication real-time thus removing the lag in process due to time spent in communicating ideas across teams.
-
+Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can help the team interactions become more fluid and clearer.
+They also make the communication real-time thus removing the delay in process due to time spent in communicating ideas across teams.
 %Integration Tools
@@
 As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
-The latter approach ideal for agile development since this approaches defines system components in terms of design dicisions, which empowers invidual teams.
+The latter approach ideal for agile development since this approaches defines system components in terms of design decisions, which empowers individual teams.

### 2019-01-21 Draft/Parts/Conclusion.tex
Finish pass on introduction.

@@
 \section{Conclusion}\label{sec:conclusion}
-As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
+As we have seen, inter-team communication can be an obstacle in agile teams working together, as intermediaries in communication and lack of personal communication causes a distruption in software process.
 To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

### 2019-01-21 Draft/Parts/Introduction.tex
Finish pass on introduction.

--- 2019-01-19 Draft/Parts/Introduction.tex
@@
-As mentioned in the Agile Manifesto \cite{beck2001agile}, Individuals and Interactions are given more value than the processes and tools.
-At the same time, an agile team is supposed to contain all that is required for them to do their work, thus interactions no matter how valuable usually are done intra-team only.
-Thus, when a situation arrives where two or more agile teams need to work together to achieve a common goal the usual approach taken by companies fail.
-The agile approach of interacting in-person fails due to a few reasons such as the vertical structure of the company organization and the existence of middle managers \cite{dzone_article}.
-This large number of intermediaries in inter team communication causes the process to crumble and fall apart as it takes longer than usual time for messages to reach their destination then what agile can afford.
-This problem is harder to fix as this is so embedded in the working culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required.
-And that’s where the approaches listed in the article comes in.
-We have collected a couple of approaches which if implemented efficiently results in a more stable and functioning agile process model.
-Thus, in the following sections we will be explaining couple of approaches we came across.
-\linebreak
-\linebreak
-In Section ~\ref{sec:proc_impv}, we will be explaining the improvements that can be made to the process and team structures to get better collaboration out of the team involved.
-\linebreak
-\linebreak
-In Section ~\ref{sec:tech_impv}, we will be explaining the enhancements that can be done in the technology stack being used and in the different ways in which technology can help in improving the process.
+%Introduction (Introducing the topic)
+
+%AM: What is the problem?
+%introduce the need to scale to multiple agile teams
+Agile approaches are popular in software development for numerous reasons.
+However, the structure of the agile process does not lend itself to large teams and is not suitable for large projects.
+With the growth in complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
+%thesis statement
+When scaling to parallel agile teams, the most important consideration is quality communication, both personal and architectural.
+%
+For an example of a company developing a complex piece of software, consider Spotify AB who has over 30 teams \cite{kniberg12}.
+Spotify is a streaming music client which supports media, commercial, and social features.
+The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
+%Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
+Squads in related areas are grouped together into Tribes. 
+The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
+\begin{figure}[h]
+  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
+  \caption{Agile team organization at Spotify \cite{kniberg12}.}
+  \label{fig:spotify_structure}
+\end{figure}
+
+%AM: Why is it interesting/important?
+%introduce agile
+As outlined in the Agile Manifesto \cite{beck2001agile}, an agile process gives individuals and interactions value over processes and tools.
+An agile team should contain all that is required for them to do their work, thus interactions are intensely intra-team.
+However, diverse feature sets such as required in the Spotify application necessitate many skillsets and substantial manpower.
+By moving to a multi-team model, complex projects can benefit from agility, provided that the process is adapted.
+%personal communication
+Multiple teams increases the importance of communication, from simple interpersonal communication to system specification. 
+The agile approach of interacting in-person can fail due to reasons such as the vertical structure of the company organization and layers of middle managers \cite{dzone_article}.
+The large number of intermediaries can cause an agile process to breakdown as it takes longer than usual time for messages to reach their destination than can afforded.
+%arch communication
+In an agile process, where Big Design Up-front may typically be avoided, the move to multiple teams motivates a need to communicate design decisions.
+%todo: component boundaries?
+For successful integration of technological components, system elements must have well defined functional specifications, and interfaces.
+
+%RA: feel like we can skip AM suggest section on Why is it hard.
+%AM: What are the key components of [the] proposed approach? Also include assumptions/limitations
+%We discuss approaches, which if implemented correctly, provide a more robust and functional process for inter-team agile development.
+
+%outline of rest of paper
+This document is organized as follows: Introduction, Communication Concerns, Supporting Communication in Inter-team Development, and Conclusion. 
+In Section ~\ref{sec:spt_ex}, we discuss example communication concerns in an agile project.
+In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help to resolve issues.
+Lastly, Section ~\ref{sec:conclusion} concludes with an overview of important aspects of inter-team agile development.
+
+%This problem is difficult to fix as this is so embedded in the working agile culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required.
+%RA: this is an important observation, just too detailed for intro.

### 2019-01-21 Draft/Parts/Main.tex
Finish pass on introduction.

@@
-\section{Spotify: A Canonical Example} 
-\label{sec:spt_ex} 
-For an example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
-The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
-Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
-Squads in related areas are grouped together into Tribes. 
-The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
+\section{Communication Concerns}\label{sec:spt_ex} 
 Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
-
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
-  \caption{Agile team organization at Spotify \cite{kniberg12}.}
-  \label{fig:spotify_structure}
-\end{figure}
-
-\subsection{Communication at Spotify}
 %social fixes
@@
 Without communication, these team members would perform redundant work.
-To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers individuals with similar roles across different Squads.
+To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads  \cite{kniberg12}.
 
-\section{Communication in Inter-team Development}
+\section{Supporting Communication in Inter-team Development}
 \label{sec:prop_appro} 
@@
 	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
-	These changes are to be made part of the entire process and are not to be implemented only in the end.
+	These changes are to be made part of the entire process.
 

### 2019-01-21 Draft/Parts/Conclusion.tex
Better conclusion.

@@
 \section{Conclusion}\label{sec:conclusion}
-As we have seen, inter-team communication can be an obstacle in agile teams working together, as intermediaries in communication and lack of personal communication causes a distruption in software process.
-To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.
+As we have seen, inter-team communication can be a significant obstacle when agile teams work together, as intermediaries in communication and lack of personal communication causes a disruption in the agile process.
+To reduce this problem a number of small adaptions can be made to the process to ensure the flow of information.
+However, the most important adaption is a well defined design and architecture which is available across teams and enables teams to produce individual system components which can be easily integrated.

### 2019-01-21 Draft/Parts/Main.tex
Finish pass on main text.

@@
 \section{Communication Concerns}\label{sec:spt_ex} 
-Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
-%social fixes
+%overview
 A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
+% problem
+Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team.
+Without communication, these team members would perform redundant work.
+To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads. 
 At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
-This leads to an environment where an informal exchange of information on the Tribes work will occur.
-%second problem
-Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team.
-Without communication, these team members would perform redundant work.
-To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads  \cite{kniberg12}.
+This leads to an environment where an informal exchange of information on the Tribe's work will occur.
+%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
+%todo: any more issues? Dunbar
+
+In general, consistency becomes as issue when expanding to multiple teams.
+The product owner in an agile process model is the person with the project vision and if it is a small team the product owner can clearly communicate this to every team member.
+Members can even query the product owner directly when in doubt.
+However, in large scale projects where multiple teams are working together, it is practically impossible for the owner to keep doing what they did in a small team.
+That’s where a formal definition of their vision is useful as it gives teams something to consult to when encountering a design decision.
 
@@
 The general problem of communication can be tackled from two perspectives.
-First, stakeholders at different levels need to have ways to pass information.
-This can be addressed by adaptions in development process and leveraging technology.
-Second, the quality of communication needs to be accurate.
-This can be addressed by sound system specification through architecture and design.
-%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
-%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
-%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.
+First, stakeholders at and across different levels need to have communication channels.
+This can be addressed by adaptations in development process and leveraging technology.
+Second, the quality (e.g., accuracy) of communication needs to be high.
+This can be addressed by thorough system specification through architecture and design.
 
-\subsection{Process Improvements} 
+\subsection{Process Adaptations} 
 \label{sec:proc_impv}
-	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
-	These changes are to be made part of the entire process.
+	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during integration.
 
 %Changes in standups
-	One of the most critical aspect of agile process model is to have daily standups which are the platform serving the purpose of letting each team member know the work being done in the other parts of the team and correlate it with the work being done by them.
-	This results in escalation of differences between the development early in the process and prevents end moment discovery of mismatches in interfaces and such.
-	In the case of multiple agile teams this problem is compounded as usually a daily stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
-	This can be resolved by having a representative of each concerned team being present in the daily standup thus letting each team know the status of other teams.
+One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
+This uncovers differences in understanding early in development and prevents last minute discovery of mismatches in development.
+In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
+This can be resolved by having a representative of each concerned team be present in the daily standup thus letting each team know the status of the other teams.
 
 %Changes to Product Owner
-Though in usual implementations the product owner is responsible for agile teams under his supervision, in large projects with multiple agile teams where a number of product owners are present sometimes over time the vision of the owners may get too distinct from each other thus pushing the development track in different directions.
-This can be limited by having regular meetings of product owners where the scope and vision of the project could be synced again.
-This can be a bi-weekly or monthly meeting depending on the size of the project.
+Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead the development in different directions.
+This can be limited by having regular meetings of product owners where the scope and vision of the project can be synchronized.
+%This can be a bi-weekly or monthly meeting depending on the size of the project.
 
 %Changes in Planning Sessions
-All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting.
+All the initial, intermediate and final planning sessions should be made such that teams which are or could be impacted by that part of the project are part of the meeting.
 This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
 
-\subsection{Technology Approaches} \label{sec:tech_impv}
-Selecting an appropriate technology stack plays an important role maintaining a widely distributed team.
-Technology can help teams in keeping track of things that they need to do so that other teams can work efficiently.
-The following are some of the areas where the technology can enable a more efficient agile process environment.
+\subsection{Technology Improvements} \label{sec:tech_impv}
+Selecting an appropriate technology stack plays an important role in maintaining a distributed development environment.
+Technology enables communication and task management so that teams can work together efficiently.
+%The following are areas where technology can enable a more efficient agile process.
 
 %Communication Tools
-Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can help the team interactions become more fluid and clearer.
-They also make the communication real-time thus removing the delay in process due to time spent in communicating ideas across teams.
+Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
+They also make communication real-time, reducing delay due to time spent in communicating ideas across teams.
 %Integration Tools
-Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.
+Continuous integration tools can go a long way in identifying inter-team problems early in development
+as it reveals the impact of changes on the entire project.
 
-\subsection{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
+\subsection{Importance of Architecture and Design}\label{sec:imp_of_dsgn}
 %Why is Design/Architecture so important when doing this?
 
-As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt.
-But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision.
-The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners.
-The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.
+System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners.
+The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
 %non specification fix
-Spotify addresses this issue with a more organizational approach by defining a "system owner" role \cite{kniberg12}.
+A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
 This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.
 
-In addition to specification of system elements, architecture can also be used to empower teams.
+In addition to specification, proper architecture can also be used to enable team agility.
 As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
-The latter approach ideal for agile development since this approaches defines system components in terms of design decisions, which empowers individual teams.
+The latter approach is ideal for agile development since it defines system components in terms of hiding design decisions, which empowers individual teams to design their own solution.

### 2019-01-21 Draft/Parts/Conclusion.tex
Many typo fixes, tone corrects, and clarifications.

@@
 \section{Conclusion}\label{sec:conclusion}
-As we have seen, inter-team communication can be a significant obstacle when agile teams work together, as intermediaries in communication and lack of personal communication causes a disruption in the agile process.
-To reduce this problem a number of small adaptions can be made to the process to ensure the flow of information.
+As we have seen, inter-team communication can be an obstacle when agile teams work together, as intermediaries in communication and lack of personal communication causes a disruption in the agile process.
+To reduce this problem a number of adaptions can be made to the process to ensure the flow of information.
 However, the most important adaption is a well defined design and architecture which is available across teams and enables teams to produce individual system components which can be easily integrated.

### 2019-01-21 Draft/Parts/Introduction.tex
Minor adjustment in intro.
Many typo fixes, tone corrects, and clarifications.

@@
 %introduce the need to scale to multiple agile teams
-Agile approaches are popular in software development for numerous reasons.
-However, the structure of the agile process does not lend itself to large teams and is not suitable for large projects.
-With the growth in complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
+Agile approaches are popular in software development for many reasons.
+However, the structure of an agile process does not lend itself to large teams and is not suitable for large projects.
+In complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
 %thesis statement
-When scaling to parallel agile teams, the most important consideration is quality communication, both personal and architectural.
+When scaling to parallel teams, the most important consideration is effective communication, both personal and architectural.
 %
@@
 An agile team should contain all that is required for them to do their work, thus interactions are intensely intra-team.
-However, diverse feature sets such as required in the Spotify application necessitate many skillsets and substantial manpower.
-By moving to a multi-team model, complex projects can benefit from agility, provided that the process is adapted.
+However, diverse feature sets such as required in the Spotify application necessitate many skill sets and substantial manpower.
+By moving to a multi-team model, large projects can benefit from agility, provided that the process is adapted.
 %personal communication
 Multiple teams increases the importance of communication, from simple interpersonal communication to system specification. 
-The agile approach of interacting in-person can fail due to reasons such as the vertical structure of the company organization and layers of middle managers \cite{dzone_article}.
-The large number of intermediaries can cause an agile process to breakdown as it takes longer than usual time for messages to reach their destination than can afforded.
+The agile approach of interacting in-person can fail due to reasons such as the vertical structure of company organization and layers of middle managers \cite{dzone_article}.
+The large number of intermediaries can cause an agile process to breakdown as it takes longer than usual for messages to reach their destination than can afforded.
 %arch communication
-In an agile process, where Big Design Up-front may typically be avoided, the move to multiple teams motivates a need to communicate design decisions.
+In an agile process, where Big Design Up Front may typically be avoided, the move to multiple teams motivates a need to communicate design decisions.
 %todo: component boundaries?
@@
 This document is organized as follows: Introduction, Communication Concerns, Supporting Communication in Inter-team Development, and Conclusion. 
-In Section ~\ref{sec:spt_ex}, we discuss example communication concerns in an agile project.
+In Section ~\ref{sec:spt_ex}, we discuss example communication concerns.
 In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help to resolve issues.

### 2019-01-21 Draft/Parts/Main.tex
Many typo fixes, tone corrects, and clarifications.

@@
 Without communication, these team members would perform redundant work.
-To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads. 
+To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
 At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
@@
 
-In general, consistency becomes as issue when expanding to multiple teams.
-The product owner in an agile process model is the person with the project vision and if it is a small team the product owner can clearly communicate this to every team member.
+In general, consistency becomes an issue when expanding to multiple teams.
+The product owner in an agile process model is the person with the project vision, and with a small team, the product owner can clearly communicate this to every team member.
 Members can even query the product owner directly when in doubt.
-However, in large scale projects where multiple teams are working together, it is practically impossible for the owner to keep doing what they did in a small team.
-That’s where a formal definition of their vision is useful as it gives teams something to consult to when encountering a design decision.
+However, in large projects where multiple teams are working together, it is practically impossible for the owner to continue what they did in a small team.
+This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
 
@@
 Second, the quality (e.g., accuracy) of communication needs to be high.
-This can be addressed by thorough system specification through architecture and design.
+This can be addressed by thorough system specification through architecture.
 
@@
 One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
-This uncovers differences in understanding early in development and prevents last minute discovery of mismatches in development.
+This uncovers differences in understanding early in development and prevents last minute discovery of discrepancies.
 In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
@@
 %Changes to Product Owner
-Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead the development in different directions.
+Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and so over time the vision of the owners may drift and lead the development in different directions.
 This can be limited by having regular meetings of product owners where the scope and vision of the project can be synchronized.
@@
 %Changes in Planning Sessions
-All the initial, intermediate and final planning sessions should be made such that teams which are or could be impacted by that part of the project are part of the meeting.
+All the initial, intermediate and final planning sessions should be organized such that teams which are, or could be, impacted by that part of the project are part of the meeting.
 This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
@@
 Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
-They also make communication real-time, reducing delay due to time spent in communicating ideas across teams.
+They also make communication real-time, reducing delay due to time spent communicating ideas across teams.
 %Integration Tools
@@
 
-System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners.
+System design and architecture acts as a common vision for not only teams but also for the communication between all the product owners.
 The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
@@
 A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
-This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.
+This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain a long term stewardship over a sub-system.
 

### 2019-01-21 Draft/Parts/Main.tex
Finishing half thoughts.

@@
 %overview
-A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
+A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
 % problem
@@
 This leads to an environment where an informal exchange of information on the Tribe's work will occur.
-%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
+Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
 %todo: any more issues? Dunbar
@@
 This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
+Without a functional specification, teams will be unable to produce components which can be integrated.
 
@@
 \label{sec:proc_impv}
-	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during integration.
+	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during development or integration.
 
@@
 \subsection{Technology Improvements} \label{sec:tech_impv}
-Selecting an appropriate technology stack plays an important role in maintaining a distributed development environment.
-Technology enables communication and task management so that teams can work together efficiently.
+Selecting an appropriate technology stack plays an important role in enabling communication and task management so that teams can work together efficiently.
 %The following are areas where technology can enable a more efficient agile process.

### 2019-01-21 Draft/Parts/Main.tex
Added SOS ref.

@@
 This leads to an environment where an informal exchange of information on the Tribe's work will occur.
-Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
+%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
 %todo: any more issues? Dunbar
@@
 In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
-This can be resolved by having a representative of each concerned team be present in the daily standup thus letting each team know the status of the other teams.
+This can be resolved by having a representative of each team be present in a standup, e.g., a Scrum of Scrums, where typical stand up questions are given but reframed for a team context (e.g., "What will my team do before we meet again.." \cite{Rubin12}).
 

### 2019-01-21 Draft/Parts/Conclusion.tex
Polish.

@@
 \section{Conclusion}\label{sec:conclusion}
-As we have seen, inter-team communication can be an obstacle when agile teams work together, as intermediaries in communication and lack of personal communication causes a disruption in the agile process.
+As we have seen, inter-team communication can be an obstacle when agile teams work together, as intermediaries in communication and lack of personal communication causes disruption in the agile process.
 To reduce this problem a number of adaptions can be made to the process to ensure the flow of information.

### 2019-01-21 Draft/Parts/Introduction.tex
Finishing half thoughts.
Polish.

@@
 Agile approaches are popular in software development for many reasons.
-However, the structure of an agile process does not lend itself to large teams and is not suitable for large projects.
+However, the structure of an agile process does not lend itself to large teams and is not suitable for large projects \cite{Rubin12}.
 In complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
 %thesis statement
-When scaling to parallel teams, the most important consideration is effective communication, both personal and architectural.
+When scaling to multiple teams, the most important consideration is enabling effective communication, both personal and architectural, which is the focus of this paper.
 %
@@
 However, diverse feature sets such as required in the Spotify application necessitate many skill sets and substantial manpower.
-By moving to a multi-team model, large projects can benefit from agility, provided that the process is adapted.
+By using a multi-team model, large projects can benefit from agility, provided that the process is adapted.
 %personal communication
@@
 %arch communication
-In an agile process, where Big Design Up Front may typically be avoided, the move to multiple teams motivates a need to communicate design decisions.
+In an agile process, where Big Design Up Front may typically be avoided, the move to multiple teams also motivates a need to communicate design decisions.
 %todo: component boundaries?
@@
 In Section ~\ref{sec:spt_ex}, we discuss example communication concerns.
-In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help to resolve issues.
+In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help resolve issues.
 Lastly, Section ~\ref{sec:conclusion} concludes with an overview of important aspects of inter-team agile development.

### 2019-01-21 Draft/Parts/Main.tex
Polish.

@@
 % problem
-Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team.
+Consider a scenario at Spotify \cite{kniberg12}: a tester in a particular Squad invested time to solve a particular problem, which was also faced by another tester on a different team.
 Without communication, these team members would perform redundant work.
 To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
-At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
+At Spotify, offices are laid out so that the Squads making up a Tribe are spatially close \cite{kniberg12}.
 This leads to an environment where an informal exchange of information on the Tribe's work will occur.
@@
 
-In general, consistency becomes an issue when expanding to multiple teams.
-The product owner in an agile process model is the person with the project vision, and with a small team, the product owner can clearly communicate this to every team member.
+Consistency becomes an issue when expanding to multiple teams.
+The product owner in an agile process model is the person with the project vision, and with a small team, they can clearly communicate it to every team member.
 Members can even query the product owner directly when in doubt.
@@
 This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
-Without a functional specification, teams will be unable to produce components which can be integrated.
+Without a functional specification, teams will be unable to produce components which can be easily integrated.
 
@@
 %Communication Tools
-Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
+Since agile focuses on interactions, like face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
 They also make communication real-time, reducing delay due to time spent communicating ideas across teams.
@@
 
-System design and architecture acts as a common vision for not only teams but also for the communication between all the product owners.
-The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
+System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners.
+The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
 %non specification fix

### 2019-02-03 Draft/Parts/Introduction.tex
Updated introduction and section 3.3 to incorporate reviews

--- 2019-01-21 Draft/Parts/Introduction.tex
@@
 %introduce the need to scale to multiple agile teams
-Agile approaches are popular in software development for numerous reasons.
+Agile approaches are popular in software development for numerous reasons such as its adaptability towards change in requirements, early customer satisfaction and increase in team effectiveness with time.
 However, the structure of the agile process does not lend itself to large teams and is not suitable for large projects.

### 2019-02-03 Draft/Parts/Main.tex
Updated introduction and section 3.3 to incorporate reviews

--- 2019-01-21 Draft/Parts/Main.tex
@@
 %overview
-A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
+A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
 % problem
@@
 Without communication, these team members would perform redundant work.
-To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
+To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads. 
 At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
 This leads to an environment where an informal exchange of information on the Tribe's work will occur.
-Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
+%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
 %todo: any more issues? Dunbar
 
-In general, consistency becomes an issue when expanding to multiple teams.
-The product owner in an agile process model is the person with the project vision, and with a small team, the product owner can clearly communicate this to every team member.
+In general, consistency becomes as issue when expanding to multiple teams.
+The product owner in an agile process model is the person with the project vision and if it is a small team the product owner can clearly communicate this to every team member.
 Members can even query the product owner directly when in doubt.
-However, in large projects where multiple teams are working together, it is practically impossible for the owner to continue what they did in a small team.
-This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
-Without a functional specification, teams will be unable to produce components which can be integrated.
+However, in large scale projects where multiple teams are working together, it is practically impossible for the owner to keep doing what they did in a small team.
+That’s where a formal definition of their vision is useful as it gives teams something to consult to when encountering a design decision.
 
@@
 Second, the quality (e.g., accuracy) of communication needs to be high.
-This can be addressed by thorough system specification through architecture.
+This can be addressed by thorough system specification through architecture and design.
 
@@
 \label{sec:proc_impv}
-	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during development or integration.
+	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during integration.
 
@@
 One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
-This uncovers differences in understanding early in development and prevents last minute discovery of discrepancies.
+This uncovers differences in understanding early in development and prevents last minute discovery of mismatches in development.
 In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
@@
 %Changes to Product Owner
-Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and so over time the vision of the owners may drift and lead the development in different directions.
+Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead the development in different directions.
 This can be limited by having regular meetings of product owners where the scope and vision of the project can be synchronized.
@@
 %Changes in Planning Sessions
-All the initial, intermediate and final planning sessions should be organized such that teams which are, or could be, impacted by that part of the project are part of the meeting.
+All the initial, intermediate and final planning sessions should be made such that teams which are or could be impacted by that part of the project are part of the meeting.
 This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.
@@
 \subsection{Technology Improvements} \label{sec:tech_impv}
-Selecting an appropriate technology stack plays an important role in enabling communication and task management so that teams can work together efficiently.
+Selecting an appropriate technology stack plays an important role in maintaining a distributed development environment.
+Technology enables communication and task management so that teams can work together efficiently.
 %The following are areas where technology can enable a more efficient agile process.
@@
 Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
-They also make communication real-time, reducing delay due to time spent communicating ideas across teams.
+They also make communication real-time, reducing delay due to time spent in communicating ideas across teams.
 %Integration Tools
@@
 
-System design and architecture acts as a common vision for not only teams but also for the communication between all the product owners.
-The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
+System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
+Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
 %non specification fix
 A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
-This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain a long term stewardship over a sub-system.
+This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.
 
@@
 The latter approach is ideal for agile development since it defines system components in terms of hiding design decisions, which empowers individual teams to design their own solution.
+
+Another way in which a formal architecture description helps in mitigating the communication problems is by minimizing the need for inter-team communication as a good design document is clear enough for a developer to incorporate the design in the system without the need of any other document.
+Thus, a good design documents sometimes acts as a proxy for product owner when it comes to detailing the requirements of the customer.

### 2019-02-03 Draft/Parts/Main.tex

--- 2019-01-21 Draft/Parts/Main.tex
@@
 
-System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners.
-The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
+System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
+Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
+System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
+Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
 %non specification fix

### 2019-02-03 Draft/Parts/Main.tex
Fixed some editing issues in 3.3

@@
 System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
-Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
-System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
 Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.

### 2019-02-04 Draft/Parts/Introduction.tex
Many minor changes. Mainly for length.

--- 2019-01-21 Draft/Parts/Introduction.tex
@@
 %introduce the need to scale to multiple agile teams
-Agile approaches are popular in software development for many reasons.
-However, the structure of an agile process does not lend itself to large teams and is not suitable for large projects \cite{Rubin12}.
+Agile approaches are popular in software development for many reasons such as adaptability towards change, early customer satisfaction, and increase in team effectiveness with time.
+However, the concept of an agile process does not lend itself to large teams and is not suitable for large projects \cite{Rubin12}.
 In complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
@@
 %personal communication
-Multiple teams increases the importance of communication, from simple interpersonal communication to system specification. 
-The agile approach of interacting in-person can fail due to reasons such as the vertical structure of company organization and layers of middle managers \cite{dzone_article}.
-The large number of intermediaries can cause an agile process to breakdown as it takes longer than usual for messages to reach their destination than can afforded.
+Multiple teams increases the importance of communication, from interpersonal to system specification. 
+The agile approach of interacting in-person can fail due to reasons such as the vertical nature of a company and layers of middle managers \cite{dzone_article}.
+The large number of intermediaries can cause an agile process to breakdown as it takes longer for messages to reach their destination than can be afforded.
 %arch communication
-In an agile process, where Big Design Up Front may typically be avoided, the move to multiple teams also motivates a need to communicate design decisions.
+In agile, where Big Design Up Front may be avoided, the move to multiple teams also motivates a need to communicate design. %decisions
 %todo: component boundaries?
-For successful integration of technological components, system elements must have well defined functional specifications, and interfaces.
+For successful integration of components, system elements must have well defined functional specifications and interfaces.
 
@@
 This document is organized as follows: Introduction, Communication Concerns, Supporting Communication in Inter-team Development, and Conclusion. 
-In Section ~\ref{sec:spt_ex}, we discuss example communication concerns.
-In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help resolve issues.
-Lastly, Section ~\ref{sec:conclusion} concludes with an overview of important aspects of inter-team agile development.
+In Section ~\ref{sec:spt_ex}, we discuss communication issues.
+In Section ~\ref{sec:prop_appro}, we present process adaptations that can help resolve issues.
+Section ~\ref{sec:conclusion} concludes with an overview of key aspects of inter-team agile development.
 

### 2019-02-04 Draft/Parts/Main.tex
Many minor changes. Mainly for length.

@@
 % problem
-Consider a scenario at Spotify \cite{kniberg12}: a tester in a particular Squad invested time to solve a particular problem, which was also faced by another tester on a different team.
-Without communication, these team members would perform redundant work.
+Consider a scenario at Spotify \cite{kniberg12}: a tester in a particular Squad invested time to solve a problem, which was also faced by another tester on a different team.
+Without communication, members would perform redundant work.
 To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
@@
 Consistency becomes an issue when expanding to multiple teams.
-The product owner in an agile process model is the person with the project vision, and with a small team, they can clearly communicate it to every team member.
-Members can even query the product owner directly when in doubt.
-However, in large projects where multiple teams are working together, it is practically impossible for the owner to continue what they did in a small team.
+The product owner in an agile process model is the person with the project vision.
+In a small team, they can clearly communicate it to every team member, and
+members can even query the product owner.
+However, in large projects with multiple teams, it is practically impossible for the owner to continue what they did in a small team.
 This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
@@
 %Changes in standups
-One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
-This uncovers differences in understanding early in development and prevents last minute discovery of discrepancies.
-In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
-This can be resolved by having a representative of each team be present in a standup, e.g., a Scrum of Scrums, where typical stand up questions are given but reframed for a team context (e.g., "What will my team do before we meet again.." \cite{Rubin12}).
+One aspect of an agile process is daily standups which are a platform for letting each team member know the work being done by other team members. % and correlate it with their work.
+This uncovers differences in understanding early and prevents last minute discovery of discrepancies.
+For multiple teams, this problem is compounded as a stand up is a closed activity, preventing other teams from knowing the discussions of each other.
+This can be resolved by having a representative from each team be present in a standup, e.g., a Scrum of Scrums, where stand up questions are given but reframed for a team \cite{Rubin12}.
 
 %Changes to Product Owner
-Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and so over time the vision of the owners may drift and lead the development in different directions.
-This can be limited by having regular meetings of product owners where the scope and vision of the project can be synchronized.
-%This can be a bi-weekly or monthly meeting depending on the size of the project.
+Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead in different directions.
+This can be limited by regular meetings of product owners where the scope and vision of the project can be synchronized.
 
@@
 \subsection{Technology Improvements} \label{sec:tech_impv}
-Selecting an appropriate technology stack plays an important role in enabling communication and task management so that teams can work together efficiently.
-%The following are areas where technology can enable a more efficient agile process.
-
+Selecting appropriate technology plays an important role in enabling communication and task management so that teams can work together efficiently.
+%
 %Communication Tools
-Since agile focuses on interactions, like face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
-They also make communication real-time, reducing delay due to time spent communicating ideas across teams.
+Since agile focuses on interactions, like face-to-face conversation, conferencing tools can lower the bar to inter-team interactions.
+They make communication real-time, reducing delay in communicating ideas across teams.
 %Integration Tools
-Continuous integration tools can go a long way in identifying inter-team problems early in development
-as it reveals the impact of changes on the entire project.
+Continuous integration tools can go a long way in identifying inter-team problems early in development as it reveals the impact of changes on the entire project.
 
@@
 
-System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
-Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
+System architecture acts as a common vision for not only the teams but also for communication between the product owners, and is the main topic for most of the inter-team communication that occurs in a multi-team environment.
+%Being such a frequent piece of discussion
+It needs to be as formal, and as clearly defined as possible, as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
+%
+A formal architecture description also helps to mitigate communication problems by reducing the need for inter-team communication as a good design document provides enough guidance for a developer to incorporate their work into the system.
+Thus, a good design document sometimes acts as a proxy for a product owner when it comes to detailing the requirements of the customer.
 %non specification fix
@@
 
-In addition to specification, proper architecture can also be used to enable team agility.
+Architecture can also be used to enable team agility.
 As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
-The latter approach is ideal for agile development since it defines system components in terms of hiding design decisions, which empowers individual teams to design their own solution.
-
-Another way in which a formal architecture description helps in mitigating the communication problems is by minimizing the need for inter-team communication as a good design document is clear enough for a developer to incorporate the design in the system without the need of any other document.
-Thus, a good design documents sometimes acts as a proxy for product owner when it comes to detailing the requirements of the customer.
+The latter approach is ideal for agile development since it defines components in terms of hiding design decisions, which empowers teams to design their own solution.

### 2019-02-04 Draft/changes.tex
Added PDF on changes.

\documentclass{article}
\usepackage{graphicx}

\begin{document}

%\title{Introduction to \LaTeX{}}
%\author{Author's Name}

%\maketitle

\section{Assignment 1: Peer Review Changes}
Our paper was reviewed by four reviewers, see the following sections for information on their feedback and changes made. The average evaluation was 2.75 on a scale where 3 was a strong accept.

\subsection{V. A. Madaraju}
\begin{itemize}
    \item Overall evaluation: 3 (strong accept)
    \item Reviewer's confidence: 5 (expert)

This reviewer noted that less importance was given to the design and architecture content, however, they did not explicitly request any changes.
No changes were based based on this feedback alone (a later reviewer noted that the paper has some hanging remarks which we took to include the depth of design and architecture, which we improved).

\end{itemize}

\subsection{C. La Place}
\begin{itemize}
    \item Overall evaluation: 3 (strong accept)
    \item Reviewer's confidence: 4 (high)

This reviewer suggested that we should review our paper for any hanging remarks. They specifically indicated the beginning where we state agile is popular, but go to disadvantages instead of justifying the initial statement. We have rectified this by adding several examples of how following an agile process is beneficial. Together with the comments of V. A. Madaraju, this reviewer's comment about hanging remarks motivated us to add additional commentary on the use and importance of design and architecture.

\end{itemize}

\subsection{D. Bhattacharyya}
\begin{itemize}
    \item Overall evaluation: 2 (accept)
    \item Reviewer's confidence: 4 (high)

This reviewer suggested that sections could have been split up more effectively, or perhaps named more effectively. We reviewed our paper but felt that the existing divisions  and section names suited our work.

\end{itemize}

\subsection{J. Drumm}
\begin{itemize}
    \item Overall evaluation: 3 (strong accept)
    \item Reviewer's confidence: 3 (medium)

This reviewer suggested that we review use of the document organization section in the introduction and decide if it is appropriate. We have determined that the description of the paper's organization is appropriate.

\end{itemize}

\end{document}
